Solving Consensus with OpenFlow

### 2015-02-17 inband-STN.tex
stefan

\documentclass[11pt,pdftex,letter]{article}
%\documentclass[11pt]{llncs}
%\documentclass[11pt,pdftex]{article}
%\documentclass{sig-alternate-10pt}
%\usepackage{amsthm}
%\usepackage{algorithm}
%\usepackage[noend]{algorithmic}
\usepackage[lined,boxed,commentsnumbered]{algorithm2e}

@@

@@

\begin{abstract}
We solve consensus with OpenFlow, using multi-write
\end{abstract}

@@

@@

>>>>

%\documentclass[11pt,pdftex,letter]{article}
\documentclass[conference]{sigcomm-alternate}

%\documentclass[11pt]{llncs}
%\documentclass[11pt,pdftex]{article}
%\documentclass{sig-alternate-10pt}
%\usepackage{amsthm}
%\usepackage{algorithm}
%\usepackage[noend]{algorithmic}
\usepackage[lined,boxed,commentsnumbered]{algorithm2e}

@@

\title{Efficient Coordination of Distributed SDN Controllers:\\The Case for Multi-Write Consensus}

\title{Consistent Coordination of Distributed SDN Controllers:\\Leveraging the Consensus Power of OpenFlow}

@@

\begin{abstract}
idea: reliable and scalable SDN needs distributed control; consistent network updates
is a key challenge, especially if distributed;

idea: this paper shows that Openflow can be leveraged to provide strong consensus
abstractions! the case for the long-forgotten multi-write

idea: we show how to synchronize controllers, single update but also multiple and efficient
\end{abstract}

@@

idea: reliable and scalable SDN needs distributed control; consistent network updates
is a key challenge, especially if distributed;

\subsection{Our Contributions}

idea: this paper shows that Openflow can be leveraged to provide strong consensus
abstractions! the case for the long-forgotten multi-write

idea: we show how to synchronize controllers, single update but also multiple and efficient

\subsection{Organization}

The remainder of this paper is organized as follows.

\section{Background}

idea: multi-write consensus, a not well-known result!

@@

\section{Related Work}\label{sec:relwork}

ideas: distributed control planes

ideas: known consensus results and impossibilities

ideas: the power of in-band

\section{Conclusion}\label{sec:conclusion}

ideas: the missing link for STN, but also others
